Stack Safety as a Security Property

### 2020-07-07 main.tex
Andrew's corrections on testing definitions

\definition{Eager integrity test}
  Given two machines \apt{machine states?} $\mach$ and $\mach'$ and a contour $\contour$, these
  satisfy the \emph{eager integrity test} if their high-integrity components
  match:
  \[
    \mathit{int}_T ~ \contour ~ \mach ~ \mach' \triangleq
    \forall \component . ~
    \contour(\component) = \HIGHINT \rightarrow
    \mach(\contour) = \mach'(\contour)
    \]
\apt{Shouldn't conclusion be $m(k) = m'(k)$ ? }

\definition{Eager confidentiality test}
  Given two machine states $\mach_1$ and $\mach_2$ with stepping states and
  observations $\mach_1 \stepstoobs{\obs_1} \mach_1'$ and $\mach_2
  \stepstoobs{\obs_2} \mach_2'$ these satisfy the \emph{eager confidentiality
  test} if their observations and changed components coincide:
  \[
    \mathit{conf}_T ~ \mach_1 ~ \obs_1 ~ \mach_1' ~ \mach_2 ~ \obs_2 ~ \mach_2' ~ \triangleq
    \obs_1 = \obs_2 \wedge \forall \component . ~
   (     \mach_1(\component) \neq \mach_1'(\component)
    \vee \mach_2(\component) \neq \mach_2'(\component))
    \rightarrow \mach_1' = \mach_2'
  \]
\apt{scoping of $\forall$ is ambiguous. Anyhow, shouldn't this be
$
\forall \component . ~
   (     \mach_1(\component) \neq \mach_1'(\component)
    \vee \mach_2(\component) \neq \mach_2'(\component))
    \rightarrow \mach_1'(\component) = \mach_2'(\component)
 $ ?}
\rb{Fix notations, including for properties below.}
\newcommand{\vse}{\mathit{vse}}
\newcommand{\VSES}{\mathit{VSE}}
\newcommand{\vs}{\mathit{vs}}
\newcommand{\VSS}{\mathit{VS}}

\definition{Variant stacks}
  The testing property keeps track of execution information on a stack whose
  elements record an initial machine, an initial and current variant of the
  machine, a contour and a return map:
  $$\vse \in \VSES ::= \MACHS \times \MACHS \times \MACHS \times \CONTOURS (\MACHS \rightarrow \mathcal{P})$$
  $$\vse = (\mathit{init\_machine}(\vse), \mathit{init\_variant}(\vse), \mathit{curr\_variant}(\vse), \contour(\vse), \mathit{ret}(\vse))$$
  $$\vs \in \VSS$$
  Given the current machine state $\mach$, a stack $\vs$ is \emph{well-formed}
  with respect to it if:
  \begin{itemize}
  \item The current variant is indeed a variant of the current state.
  \item The stack is nonempty and the bottom return map is the false property.
  \item The current state is in the trace of every initial machine.
  \item The variant state is in the trace of its own initial variant.
  \item The return function is in the return map if not the last element. \rb{TODO}
  \item All contours have public registers.
  \end{itemize}

>>>>

\definition{Eager integrity test}
  Given two machine states $\mach$ and $\mach'$ and a contour $\contour$, these
  satisfy the \emph{eager integrity test} if their high-integrity components
  match:
  \[
    \mathit{int}_T ~ \contour ~ \mach ~ \mach' \triangleq
    \forall \component . ~
    \contour(\component) = \HIGHINT \rightarrow
    \mach(\component) = \mach'(\component)
    \]

\definition{Eager confidentiality test}
  Given two machine states $\mach_1$ and $\mach_2$ with stepping states and
  observations $\mach_1 \stepstoobs{\obs_1} \mach_1'$ and $\mach_2
  \stepstoobs{\obs_2} \mach_2'$ these satisfy the \emph{eager confidentiality
  test} if their observations and changed components coincide:
  \[
    \mathit{conf}_T ~ \mach_1 ~ \obs_1 ~ \mach_1' ~ \mach_2 ~ \obs_2 ~ \mach_2' ~ \triangleq
    \obs_1 = \obs_2 \wedge \forall \component . ~
   (     \mach_1(\component) \neq \mach_1'(\component)
    \vee \mach_2(\component) \neq \mach_2'(\component))
    \rightarrow \mach_1'(\component) = \mach_2'(\component)
  \]
\apt{scoping of $\forall$ is ambiguous.}
\rb{Fix notations, including for properties below.}
\newcommand{\vse}{\mathit{vse}}
\newcommand{\VSES}{\mathit{VSE}}
\newcommand{\vs}{\mathit{vs}}
\newcommand{\VSS}{\mathit{VS}}

\definition{Variant stacks}
  The testing property keeps track of execution information on a stack whose
  elements record an initial machine, an initial and current variant of the
  machine, a contour and a return map:
  $$\vse \in \VSES ::= \MACHS \times \MACHS \times \MACHS \times \CONTOURS \times 2^\MACHS)$$
  $$\vse = (\mathit{init\_machine}(\vse), \mathit{init\_variant}(\vse), \mathit{curr\_variant}(\vse), \contour(\vse), \mathit{ret}(\vse))$$
  $$\vs \in \VSS$$
  Given the current machine state $\mach$, a stack $\vs$ is \emph{well-formed}
  with respect to it if:
  \begin{itemize}
  \item The current variant is indeed a variant of the current state.
  \item The stack is nonempty and the bottom return map is the false property.
  \item The current state is in the trace of every initial machine.
  \item The variant state is in the trace of its own initial variant.
  \item The return function is in the return map if not the last element. \rb{TODO}
  \item All contours have public registers.
  \end{itemize}
